Active Learning for SAT Solver Benchmarking

### 2024-04-16 paper_jar/paper.tex
Use Springer journal template

\documentclass[runningheads]{llncs}

\usepackage[ruled,vlined,linesnumbered,norelsize]{algorithm2e}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc} % font encoding; recommended by LNCS template
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[misc]{ifsym} % letter symbol to mark corresponding author
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage[table]{xcolor}
\usepackage{orcidlink} % ORCID icon and link; has to be loaded after "xcolor" here, else "option clash"; class "llncs" also has command "\orcidID" (which only displays full ID), but camera-ready instructions state you should add icon and link yourself
\usepackage{tikz} % has to be loaded after "xcolor" here, else "option clash"

@@

@@

\title{Active Learning for SAT Solver Benchmarking}

\author{
  Tobias Fuchs~\orcidlink{0000-0001-9727-2878} (\Letter) \and
  Jakob Bach~\orcidlink{0000-0003-0301-2798} \and
  Markus Iser~\orcidlink{0000-0003-2904-232X}
}

\institute{
  Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany \\
  \email{info@tobiasfuchs.de, jakob.bach@kit.edu, markus.iser@kit.edu}
}

\authorrunning{T. Fuchs et al.} % according to sample paper of template: first names are abbreviated; if there are more than two authors, 'et al.' is used.

@@

\begin{abstract}
  Benchmarking is a crucial phase when developing algorithms.
  This also applies to solvers for the SAT (propositional satisfiability) problem.
  Benchmark selection is about choosing representative problem instances that reliably discriminate solvers based on their runtime.
  In this paper, we present a dynamic benchmark selection approach based on active learning.
  Our approach predicts the rank of a new solver among its competitors with minimum runtime and maximum rank prediction accuracy.
  We evaluated this approach on the Anniversary Track dataset from the 2022 SAT Competition.
  Our selection approach can predict the rank of a new solver after about \SI{10}{\%} of the time it would take to run the solver on all instances of this dataset, with a prediction accuracy of about \SI{92}{\%}. 
  We also discuss the importance of instance families in the selection process. 
  Overall, our tool provides a reliable way for solver engineers to determine a new solver's performance efficiently.

  \keywords{Propositional satisfiability \and Benchmarking \and Active learning}
\end{abstract}

@@

\begin{table}[tbp]
  \centering
  \caption{Comparison of features of our benchmark-selection approach, the static benchmark-selection approach by Hoos~et~al.~\cite{HoosKSS13}, the algorithm configuration system SMAC~\cite{HutterHL11}, and the active-learning approaches by Matricon et al.~\cite{MatriconAFSH21}.
  }
  \label{tab:requirements}
  ~\\[1em]
  \begin{tabular}{
    m{0.32\textwidth}
    >{\centering\arraybackslash}m{0.16\textwidth}
    >{\centering\arraybackslash}m{0.16\textwidth}
    >{\centering\arraybackslash}m{0.16\textwidth}
    >{\centering\arraybackslash}m{0.16\textwidth}
  }
    \toprule
    Feature & Hoos~\cite{HoosKSS13} & SMAC~\cite{HutterHL11} & Matricon~\cite{MatriconAFSH21} & Our approach \\
    \midrule
    Ranking/Scoring & \cmark & \xmark & (\cmark) & \cmark \\
    Runtime Minimization & \xmark & \cmark & \cmark & \cmark \\
    Incremental/Non-Random & \xmark & \xmark & \cmark & \cmark \\
    Scalability & \cmark & \cmark & \xmark & \cmark \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{figure}[tbp!]
  \centering
  \begin{tabular}[c]{ccc}
  \begin{subfigure}[b]{0.25\textwidth}
  \centering
  \resizebox{!}{2.75cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Predic. Function};
  \node at (-2.8,0.25) {$f$};
  \end{tikzpicture}
  }
  \caption{Passive.}
  \label{fig:passive}
  \end{subfigure}
  &
  \begin{subfigure}[b]{0.35\textwidth}
  \centering
  \resizebox{!}{2.75cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Predic. Function};
  \node at (-2.8,0.25) {$f$};
  \node[right] at (-1.2,2.4) {Pool};
  \draw[->, densely dashed] (-2.4,1.2) arc (-90:0:0.8);
  \draw[->, densely dashed] (-1.6,2.8) arc (0:90:0.8);
  \node[right] at (-1.6,3.135) {$x, ?$};
  \draw  (-1.6,2.4) ellipse (0.4 and 0.3);
  \draw[fill=black]  (-1.725,2.5) ellipse (0.07 and 0.07);
  \draw[fill=black]  (-1.625,2.25) ellipse (0.07 and 0.07);
  \draw[fill=black]  (-1.425,2.4) ellipse (0.07 and 0.07);
  \end{tikzpicture}
  }
  \caption{Active Pool-based.}
  \label{fig:activepool}
  \end{subfigure}
  &
  \begin{subfigure}[b]{0.35\textwidth}
  \centering
  \resizebox{!}{2.75cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Predic. Function};
  \node at (-2.8,0.25) {$f$};
  \node[right, label={[align=left]Gen.\\Model}] at (-0.75,1.88) {};
  \node[right] at (-1.3,3.135) {$x, ?$};
  \draw[->, densely dashed] (-2.4,1.2) arc (-90:90:1.2);
  \end{tikzpicture}
  }
  \caption{Active Synthesis-based.}
  \label{fig:activesynth}
  \end{subfigure}
  \end{tabular}

@@

% TODO tf: Why not regression? Bad performance
\begin{table}[htbp]
  \centering
  \caption{Regression performance of models trained on 46 instance and 27 runtime features. We report the RMSE and MAE metrics on the test sets.}
  ~\\[1em]
  \begin{tabular}{
    >{\raggedleft\arraybackslash}m{0.37\textwidth}
    >{\centering\arraybackslash}m{0.01\textwidth}
    >{\centering\arraybackslash}m{0.28\textwidth}
    >{\centering\arraybackslash}m{0.28\textwidth}
  }
    \toprule
    {Regression Models} & & {Avg. RMSE ($\pm$ std)} & {Avg. MAE ($\pm$ std)} \\
    \midrule
    Random-Forest-Regressor & & \SI{1929.84}{s} ($\pm$ \SI{1161.15}{s}) & \phantom{0}\SI{957.36}{s} ($\pm$ \SI{297.21}{s}) \\[0.4ex]
    MLP-Regressor           & & \SI{2275.20}{s} ($\pm$ \SI{1545.01}{s}) & \SI{1284.30}{s} ($\pm$ \SI{390.57}{s}) \\
    \bottomrule
  \end{tabular}
\end{table}

% TODO tf: Timeout prediction performance
\begin{table}[htbp]
  \centering
  \caption{MCC performance of models predicting timeouts. The models are trained 28 times with each solver as a target once.}
  ~\\[1em]
  \begin{tabular}{
    >{\raggedleft\arraybackslash}m{0.37\textwidth}
    >{\centering\arraybackslash}m{0.01\textwidth}
    >{\centering\arraybackslash}m{0.28\textwidth}
    >{\centering\arraybackslash}m{0.28\textwidth}
  }
    \toprule
    {Timeout Prediction Models} & & {46 Instance Features Avg. MCC ($\pm$ std)} & {46\,+\,27 Runtime Feat. Avg. MCC ($\pm$ std)} \\
    \midrule
    Stacking (QDA\,+\,RF)                 & & 0.6513 ($\pm$ 0.0458) & 0.9527 ($\pm$ 0.0292) \\[0.4ex]
    Quadratic-DA (QDA)                    & & 0.2593 ($\pm$ 0.1310) & 0.9290 ($\pm$ 0.0339) \\[0.4ex]
    Random-Forest-Classifier (RF)         & & 0.6607 ($\pm$ 0.0547) & 0.8530 ($\pm$ 0.0479) \\[0.4ex]
    Ada-Boost                             & & 0.5412 ($\pm$ 0.0612) & 0.8384 ($\pm$ 0.0444) \\[0.4ex]
    Decision-Tree                         & & 0.5980 ($\pm$ 0.0423) & 0.8059 ($\pm$ 0.0707) \\[0.4ex]
    Logistic-Regression                   & & 0.2031 ($\pm$ 0.0728) & 0.8052 ($\pm$ 0.1018) \\[0.4ex]
    $k$NN-Classifier                      & & 0.5108 ($\pm$ 0.0387) & 0.7885 ($\pm$ 0.1521) \\[0.4ex]
    MLP-Classifier                        & & 0.1293 ($\pm$ 0.0718) & 0.7760 ($\pm$ 0.1408) \\[0.4ex]
    Support-Vector-Machines               & & 0.0595 ($\pm$ 0.0554) & 0.7757 ($\pm$ 0.2149) \\[0.4ex]
    Naive-Bayes                           & & 0.1173 ($\pm$ 0.0872) & 0.7306 ($\pm$ 0.1394) \\
    \bottomrule
  \end{tabular}
\end{table}

% TODO tf: Cluster prediction performance
\begin{table}[htbp]
  \centering
  \caption{MCC performance of the best models predicting the $C_k$ clusterings.}
  \begin{subtable}{\textwidth}
    \centering
    \caption{Predicting $C_3$ clusters.}
    \begin{tabular}{
      >{\raggedleft\arraybackslash}m{0.37\textwidth}
      >{\centering\arraybackslash}m{0.01\textwidth}
      >{\centering\arraybackslash}m{0.28\textwidth}
      >{\centering\arraybackslash}m{0.28\textwidth}
    }
      \toprule
      {$C_3$ Cluster Prediction Models} & & {46\,+\,27 Runtime Feat. Avg. MCC ($\pm$ std)} & {46\,+\,27\,+\,27 Clus. Feat. Avg. MCC ($\pm$ std)} \\
      \midrule
      Stacking (QDA\,+\,RF)                 & & 0.7464 ($\pm$ 0.0497) & 0.8380 ($\pm$ 0.0634) \\[0.4ex]
      Quadratic-DA (QDA)                    & & 0.6903 ($\pm$ 0.0607) & 0.7738 ($\pm$ 0.0459) \\[0.4ex]
      Random-Forest-Classifier (RF)         & & 0.7116 ($\pm$ 0.0385) & 0.7841 ($\pm$ 0.0469) \\
      \bottomrule
    \end{tabular}
  \end{subtable}
  \begin{subtable}{\textwidth}
    \centering
    \caption{Predicting $C_4$ clusters.}
    \begin{tabular}{
      >{\raggedleft\arraybackslash}m{0.37\textwidth}
      >{\centering\arraybackslash}m{0.01\textwidth}
      >{\centering\arraybackslash}m{0.28\textwidth}
      >{\centering\arraybackslash}m{0.28\textwidth}
    }
      \toprule
      {$C_4$ Cluster Prediction Models} & & {46\,+\,27 Runtime Feat. Avg. MCC ($\pm$ std)} & {46\,+\,27\,+\,27 Clus. Feat. Avg. MCC ($\pm$ std)} \\
      \midrule
      Stacking (QDA\,+\,RF)                 & & 0.6562 ($\pm$ 0.0538) & 0.7366 ($\pm$ 0.0377) \\[0.4ex]
      Quadratic-DA (QDA)                    & & 0.6007 ($\pm$ 0.0765) & 0.6872 ($\pm$ 0.0469) \\[0.4ex]
      Random-Forest-Classifier (RF)         & & 0.6033 ($\pm$ 0.0455) & 0.6828 ($\pm$ 0.0527) \\
      \bottomrule
    \end{tabular}
  \end{subtable}
  \begin{subtable}{\textwidth}
    \centering
    \caption{Predicting $C_5$ clusters.}
    \begin{tabular}{
      >{\raggedleft\arraybackslash}m{0.37\textwidth}
      >{\centering\arraybackslash}m{0.01\textwidth}
      >{\centering\arraybackslash}m{0.28\textwidth}
      >{\centering\arraybackslash}m{0.28\textwidth}
    }
      \toprule
      {$C_5$ Cluster Prediction Models} & & {46\,+\,27 Runtime Feat. Avg. MCC ($\pm$ std)} & {46\,+\,27\,+\,27 Clus. Feat. Avg. MCC ($\pm$ std)} \\
      \midrule
      Stacking (QDA\,+\,RF)                 & & 0.5835 ($\pm$ 0.0615) & 0.6396 ($\pm$ 0.0553) \\[0.4ex]
      Quadratic-DA (QDA)                    & & 0.5508 ($\pm$ 0.0669) & 0.5881 ($\pm$ 0.0912) \\[0.4ex]
      Random-Forest-Classifier (RF)         & & 0.5420 ($\pm$ 0.0459) & 0.5895 ($\pm$ 0.0475) \\
      \bottomrule
    \end{tabular}
  \end{subtable}
\end{table}

@@

\begin{table}[t]
  \centering
  \caption{
      Performance comparison (on the full dataset) of the best-performing active-learning approaches (\emph{AL}), random sampling of the same runtime fraction with 1000 repetitions (\emph{Random}), and statically selecting the instances most frequently sampled by active-learning approaches (\emph{Most Freq.})
    }
  \label{tab:fulldataset}

>>>>

\documentclass{sn-jnl}

\usepackage[ruled,vlined,linesnumbered,norelsize]{algorithm2e}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsthm}
\usepackage[T1]{fontenc} % font encoding; recommended by LNCS template
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[misc]{ifsym} % letter symbol to mark corresponding author
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{orcidlink} % ORCID icon and link; has to be loaded after "xcolor" here, else "option clash"; class "llncs" also has command "\orcidID" (which only displays full ID), but camera-ready instructions state you should add icon and link yourself
\usepackage{tikz} % has to be loaded after "xcolor" here, else "option clash"

@@

%% as per the requirement new theorem styles can be included as shown below
\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}% 
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}%

\raggedbottom

@@

\title[Active Learning for SAT Solver Benchmarking]{Active Learning for SAT Solver Benchmarking}

\author{\fnm{Tobias} \sur{Fuchs}}\email{tobias.fuchs@kit.edu}
\author{\fnm{Jakob} \sur{Bach}}\email{jakob.bach@kit.edu}
\author{\fnm{Markus} \sur{Iser}}\email{markus.iser@kit.edu}

\affil{\orgname{Karlsruhe Institute of Technology}, \orgaddress{\city{Karlsruhe}, \country{Germany}}}

\abstract{
  Benchmarking is a crucial phase when developing algorithms.
  This also applies to solvers for the SAT (propositional satisfiability) problem.
  Benchmark selection is about choosing representative problem instances that reliably discriminate solvers based on their runtime.
  In this paper, we present a dynamic benchmark selection approach based on active learning.
  Our approach predicts the rank of a new solver among its competitors with minimum runtime and maximum rank prediction accuracy.
  We evaluated this approach on the Anniversary Track dataset from the 2022 SAT Competition.
  Our selection approach can predict the rank of a new solver after about \SI{10}{\%} of the time it would take to run the solver on all instances of this dataset, with a prediction accuracy of about \SI{92}{\%}. 
  We also discuss the importance of instance families in the selection process. 
  Overall, our tool provides a reliable way for solver engineers to determine a new solver's performance efficiently.
}

\keywords{Propositional satisfiability, Benchmarking, Active learning}

@@

@@

\begin{table}[tbp]
  \centering
  \caption{Comparison of features of our benchmark-selection approach, the static benchmark-selection approach by Hoos~et~al.~\cite{HoosKSS13}, the algorithm configuration system SMAC~\cite{HutterHL11}, and the active-learning approaches by Matricon et al.~\cite{MatriconAFSH21}.
  }
  \label{tab:requirements}
  \begin{tabular}{
    m{0.2752\textwidth}
    >{\centering\arraybackslash}m{0.1376\textwidth}
    >{\centering\arraybackslash}m{0.1376\textwidth}
    >{\centering\arraybackslash}m{0.1376\textwidth}
    >{\centering\arraybackslash}m{0.1376\textwidth}
  }
    \toprule
    Feature & Hoos~\cite{HoosKSS13} & SMAC~\cite{HutterHL11} & Matricon~\cite{MatriconAFSH21} & Our approach \\
    \midrule
    Ranking/Scoring & \cmark & \xmark & (\cmark) & \cmark \\
    Runtime Minimization & \xmark & \cmark & \cmark & \cmark \\
    Incremental/Non-Random & \xmark & \xmark & \cmark & \cmark \\
    Scalability & \cmark & \cmark & \xmark & \cmark \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{figure}[tbp!]
  \centering
  \begin{tabular}[c]{ccc}
  \begin{subfigure}[b]{0.236\textwidth}
  \centering
  \resizebox{!}{2.75cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Predic. Function};
  \node at (-2.8,0.25) {$f$};
  \end{tikzpicture}
  }
  \caption{Passive.}
  \label{fig:passive}
  \end{subfigure}
  &
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \resizebox{!}{2.75cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Predic. Function};
  \node at (-2.8,0.25) {$f$};
  \node[right] at (-1.2,2.4) {Pool};
  \draw[->, densely dashed] (-2.4,1.2) arc (-90:0:0.8);
  \draw[->, densely dashed] (-1.6,2.8) arc (0:90:0.8);
  \node[right] at (-1.6,3.135) {$x, ?$};
  \draw  (-1.6,2.4) ellipse (0.4 and 0.3);
  \draw[fill=black]  (-1.725,2.5) ellipse (0.07 and 0.07);
  \draw[fill=black]  (-1.625,2.25) ellipse (0.07 and 0.07);
  \draw[fill=black]  (-1.425,2.4) ellipse (0.07 and 0.07);
  \end{tikzpicture}
  }
  \caption{Active Pool-based.}
  \label{fig:activepool}
  \end{subfigure}
  &
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \resizebox{!}{2.75cm}{
  \begin{tikzpicture}
  \draw[fill=black]  (-2.8,3.7) ellipse (0.1 and 0.1);
  \draw[fill=black]  (-2.6,3.4) arc (0:180:0.2);
  \node[right] at (-5.9,3.6) {Agent (Solver)};
  \draw[fill=white]  (-3.3,2.8) rectangle (-2.5,2.2);
  \draw[fill=white]  (-3.2,2.7) rectangle (-2.4,2.1);
  \draw[fill=white]  (-3.1,2.6) rectangle (-2.3,2);
  \node[right] at (-5.9,2.4) {Training Data};
  \node (v1) at (-2.8,3.4) {};
  \node (v2) at (-2.8,2.8) {};
  \draw[->]  (v1) edge (v2);
  \node[right] at (-2.8,3.1) {$x, y$};
  \node (v3) at (-2.8,2) {};
  \node (v4) at (-2.8,1.4) {};
  \draw[->]  (v3) edge (v4);
  \draw  (-3.1,1.4) rectangle (-2.5,1);
  \draw  (-2.4,3.2) rectangle (-2.4,3.2);
  \node[right] at (-5.9,1.2) {Learning Alg.};
  \node (v5) at (-2.8,1) {};
  \node (v6) at (-2.8,0.4) {};
  \draw[->]  (v5) edge (v6);
  \node[right] at (-5.9,0.25) {Predic. Function};
  \node at (-2.8,0.25) {$f$};
  \node[right, label={[align=left]Gen.\\Model}] at (-0.75,1.88) {};
  \node[right] at (-1.3,3.135) {$x, ?$};
  \draw[->, densely dashed] (-2.4,1.2) arc (-90:90:1.2);
  \end{tikzpicture}
  }
  \caption{Active Synthesis-based.}
  \label{fig:activesynth}
  \end{subfigure}
  \end{tabular}

@@

% TODO tf: Why not regression? Bad performance
\begin{table}[htbp]
  \centering
  \caption{Regression performance of models trained on 46 instance and 27 runtime features. We report the RMSE and MAE metrics on the test sets.}
  \begin{tabular}{
    >{\raggedleft\arraybackslash}m{0.33855\textwidth}
    >{\centering\arraybackslash}m{0.01\textwidth}
    >{\centering\arraybackslash}m{0.2562\textwidth}
    >{\centering\arraybackslash}m{0.2562\textwidth}
  }
    \toprule
    {Regression Models} & & {Avg. RMSE ($\pm$ std)} & {Avg. MAE ($\pm$ std)} \\
    \midrule
    Random-Forest-Regressor & & \SI{1929.84}{s} ($\pm$ \SI{1161.15}{s}) & \phantom{0}\SI{957.36}{s} ($\pm$ \SI{297.21}{s}) \\[0.4ex]
    MLP-Regressor           & & \SI{2275.20}{s} ($\pm$ \SI{1545.01}{s}) & \SI{1284.30}{s} ($\pm$ \SI{390.57}{s}) \\
    \bottomrule
  \end{tabular}
\end{table}

% TODO tf: Timeout prediction performance
\begin{table}[htbp]
  \centering
  \caption{MCC performance of models predicting timeouts. The models are trained 28 times with each solver as a target once.}
  ~\\[1em]
  \begin{tabular}{
    >{\raggedleft\arraybackslash}m{0.33855\textwidth}
    >{\centering\arraybackslash}m{0.01\textwidth}
    >{\centering\arraybackslash}m{0.2562\textwidth}
    >{\centering\arraybackslash}m{0.2562\textwidth}
  }
    \toprule
    {Timeout Prediction Models} & & {46 Instance Features Avg. MCC ($\pm$ std)} & {46\,+\,27 Runtime Feat. Avg. MCC ($\pm$ std)} \\
    \midrule
    Stacking (QDA\,+\,RF)                 & & 0.6513 ($\pm$ 0.0458) & 0.9527 ($\pm$ 0.0292) \\[0.4ex]
    Quadratic-DA (QDA)                    & & 0.2593 ($\pm$ 0.1310) & 0.9290 ($\pm$ 0.0339) \\[0.4ex]
    Random-Forest-Classifier (RF)         & & 0.6607 ($\pm$ 0.0547) & 0.8530 ($\pm$ 0.0479) \\[0.4ex]
    Ada-Boost                             & & 0.5412 ($\pm$ 0.0612) & 0.8384 ($\pm$ 0.0444) \\[0.4ex]
    Decision-Tree                         & & 0.5980 ($\pm$ 0.0423) & 0.8059 ($\pm$ 0.0707) \\[0.4ex]
    Logistic-Regression                   & & 0.2031 ($\pm$ 0.0728) & 0.8052 ($\pm$ 0.1018) \\[0.4ex]
    $k$NN-Classifier                      & & 0.5108 ($\pm$ 0.0387) & 0.7885 ($\pm$ 0.1521) \\[0.4ex]
    MLP-Classifier                        & & 0.1293 ($\pm$ 0.0718) & 0.7760 ($\pm$ 0.1408) \\[0.4ex]
    Support-Vector-Machines               & & 0.0595 ($\pm$ 0.0554) & 0.7757 ($\pm$ 0.2149) \\[0.4ex]
    Naive-Bayes                           & & 0.1173 ($\pm$ 0.0872) & 0.7306 ($\pm$ 0.1394) \\
    \bottomrule
  \end{tabular}
\end{table}

% TODO tf: Cluster prediction performance
\begin{table}[htbp]
  \centering
  \caption{MCC performance of the best models predicting the $C_k$ clusterings.}
  \begin{tabular}{
    >{\raggedleft\arraybackslash}m{0.33855\textwidth}
    >{\centering\arraybackslash}m{0.01\textwidth}
    >{\centering\arraybackslash}m{0.2562\textwidth}
    >{\centering\arraybackslash}m{0.2562\textwidth}
  }
    \toprule
    {$C_3$ Cluster Prediction Models} & & {46\,+\,27 Runtime Feat. Avg. MCC ($\pm$ std)} & {46\,+\,27\,+\,27 Clus. Feat. Avg. MCC ($\pm$ std)} \\
    \midrule
    Stacking (QDA\,+\,RF)                 & & 0.7464 ($\pm$ 0.0497) & 0.8380 ($\pm$ 0.0634) \\[0.4ex]
    Quadratic-DA (QDA)                    & & 0.6903 ($\pm$ 0.0607) & 0.7738 ($\pm$ 0.0459) \\[0.4ex]
    Random-Forest-Classifier (RF)         & & 0.7116 ($\pm$ 0.0385) & 0.7841 ($\pm$ 0.0469) \\[0.4ex]
    \midrule
    {$C_4$ Cluster Prediction Models} & & {46\,+\,27 Runtime Feat. Avg. MCC ($\pm$ std)} & {46\,+\,27\,+\,27 Clus. Feat. Avg. MCC ($\pm$ std)} \\
    \midrule
    Stacking (QDA\,+\,RF)                 & & 0.6562 ($\pm$ 0.0538) & 0.7366 ($\pm$ 0.0377) \\[0.4ex]
    Quadratic-DA (QDA)                    & & 0.6007 ($\pm$ 0.0765) & 0.6872 ($\pm$ 0.0469) \\[0.4ex]
    Random-Forest-Classifier (RF)         & & 0.6033 ($\pm$ 0.0455) & 0.6828 ($\pm$ 0.0527) \\[0.4ex]
    \midrule
    {$C_5$ Cluster Prediction Models} & & {46\,+\,27 Runtime Feat. Avg. MCC ($\pm$ std)} & {46\,+\,27\,+\,27 Clus. Feat. Avg. MCC ($\pm$ std)} \\
    \midrule
    Stacking (QDA\,+\,RF)                 & & 0.5835 ($\pm$ 0.0615) & 0.6396 ($\pm$ 0.0553) \\[0.4ex]
    Quadratic-DA (QDA)                    & & 0.5508 ($\pm$ 0.0669) & 0.5881 ($\pm$ 0.0912) \\[0.4ex]
    Random-Forest-Classifier (RF)         & & 0.5420 ($\pm$ 0.0459) & 0.5895 ($\pm$ 0.0475) \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[tp]
  \centering
  \caption{
    Performance comparison (on the full dataset) of the best-performing AL approach (\emph{AL}), random sampling of the same runtime fraction with 1000 repetitions (\emph{Random}), and statically selecting the instances most frequently sampled by active-learning approaches (\emph{Most Frequent})
  }
  \label{tab:fulldataset}
  \begin{tabular}{
    >{\arraybackslash}p{0.4\textwidth}
    S[table-format=2.2,table-column-width=0.15\textwidth]
    S[table-format=2.2,table-column-width=0.15\textwidth]
    S[table-format=2.2,table-column-width=0.15\textwidth]
  }
    \toprule
    {For $\delta \in \left[0.2, 0.7\right]$} & {AL} & {Random} & {Most Frequent} \\
    \midrule
    Sampled Runtime Fraction (\%) & 5.41 & 5.43 & 5.44 \\
    Sampled Instance Fraction (\%) & 26.53 & 5.43 & 27.75 \\
    Ranking Accuracy (\%) & 90.48 & 88.54 & 81.08 \\
    \midrule
    {For $\delta \in (0.7, 0.8]$}  & {AL} & {Random} & {Most Frequent} \\
    \midrule
    Sampled Runtime Fraction (\%) & 10.35 & 10.37 & 10.37 \\
    Sampled Instance Fraction (\%) & 5.24 & 10.37 & 36.96 \\
    Ranking Accuracy (\%) & 92.33 & 91.61 & 84.52 \\
    \bottomrule
  \end{tabular}
\end{table}
